\documentclass[11pt]{scrartcl}

\title{\textbf{Legal Aspects}}
\subtitle{Intellectual Property: Chihuly's Lawsuit}
\author{Miguel Vidal}
\date{\today}

\begin{document}

\maketitle

\section{Summary}

\begin{itemize}

	\item School of knowledgement.
	\item nature inspiration.
	\item influence, quotation.
\end{itemize}

\section{Enunciate}

Please, read the article about \emph{Chihuly's Lawsuit}\footnote{http://seattletimes.com/html/localnews/2002686721\_chihuly16m.html} and then answer:

\begin{itemize}

	\item What did Chihuly claim (and why)?\\
	
		\emph{"The copyright-infringement suit, filed Oct. 27 by Seattle-based Chihuly Inc. and the world-renowned glass artist's publishing company, is asking for at least \$1 million in damages."}
		\emph{Chihuly} wants its work will be recognized and the problem of confusing art buyers when they buy another piece thinking that is an originall Chihuly.
	\item What did the defendants allege?\\
	
		The defense position is that \emph{"if the plaintiffs cannot identify the ... infringing work, then they have no business bringing a copyright-infringement claim in the first place"}, that the concept could be similar so there is no copyright violation.
	\item Do you think the influence, imitation or inspiration of another artist may be subject to copyright? Explain your point of view.\\
	
		No, I don't think so because everyone is inspired, influenced and imites all that surround him/her. A brief example is when you start to play an instrument, you start playing songs you like and you will create music just like the one you love. Moreover like the article says about surrealist and impressionist schools of art, all are influences from people, these disciplines someday were born from a person and then become schools and influence more people to do things like they do in the past.
		
	\item In which sense can be said (based on this case) exercising intellectual property often requires violation of other individual property rights?\\
	
		Applying this expression, \emph{Bryan Rubino} holds intellectual property from its past experience violating individual property rights selling his art as \emph{Chihuly}'s through \emph{Robert Kaindl}.
		
\end{itemize}

\begin{thebibliography}{9}

\bibitem{lamport94}
  Maureen O'Hagan,\\
  Seattle Times staff reporter.\\
  http://seattletimes.com/html/localnews/2002686721\_chihuly16m.html

\end{thebibliography}
\end{document}
