\documentclass[11pt]{scrartcl}

\title{\textbf{Legal Aspects}}
\subtitle{Intellectual Property: The SCO Group lawsuit against Linux}
\author{Miguel Vidal}
\date{\today}

\begin{document}

\maketitle

\section{Exercise}

In 2003 SCO Group claimed a cluster of legal complaints about Unix and Linux source code:
 
\begin{enumerate}

	\item What alleged IP violations SCO claimed? ¿What companies was involved?

		\begin{itemize}
			\item IBM wrote and donated to be incorporated into Linux was added in violation of SCO's contractual rights.
			\item \emph{SCO Group filed suit against IBM for \$1 Billion (later raised to \$3 Billion) on unsubstantiated charges of having transferred SCO intellectual property to the Linux community in violation of IBM's license for AIX Unix, through which IBM had access to SCO's source code. SCO claims attempts to negotiate with IBM were fruitless. IBM says they were never approached at all on the matter.}\footnote{http://www.aaxnet.com/editor/edit032.html\#ibm}.
			
			\item \textbf{Answer}: as a conclusion, SCO claimed to be the owner of Unix copyrights and intellectual property of Unix therefore Linux that is Unix heritage breaks intellectual property rights using IBM's donations from Unix into Linux distributions.

			\item \emph{IBM, Novell and Red Hat claimed against SCO} to defend its rights and the users. FSF is not a company.
		\end{itemize}
		
	\item How the SCO litigation was resolved? What was the final verdict?

	\emph{Novell, not the SCO Group, is the rightful owner of the copyrights covering the Unix operating system. The court also ruled that "SCO is obligated to recognise Novell's waiver of SCO's claims against IBM and Sequent}\footnote{http://www.groklaw.net/article.php?story=20081120195227418}.\\
	SCO was not the owner of Unix copyrights so this company has no rights to do nothing against the users and the other companies involved. Novell was declared as the official owner of intellectual property and didn't want to purse Unix copyrights\footnote{http://www.pcworld.com/article/135959/article.html}.

	\item Now, search the Web and read "Open Letter"\footnote{http://www.sco.com/copyright/} from Darl McBride, CEO of SCO, dated December 4, 2003:	

	\begin{enumerate}
		\item What does the letter argue about copyleft scheme and GPL license?
			\begin{itemize}
				\item \emph{increasingly rancorous legal controversy over violations of our UNIX intellectual property contract, and what we assert is the widespread presence of our copyrighted UNIX code in Linux}
				\item \emph{U.S. copyright law versus the GNU GPL}.
				\item patent laws
				\item "the motive of profit is the engine that ensures the progress of science."
				
				\textbf{Answer}: the main argue about copyleft and GPL license is that USA always claims about copyright for science improvements and using this kind of 'rights' could be the worst decision ever and will make the country lots of damages to innovation and investigation. Defines GPL and copyleft as evil, that wants to steal the ideas of the people and taking profit without any consideration of the investigator that is bare in front of this model without patterns. \emph{Pattern} is the word that is more used to defend copyright in this letter, as the old fashioned way to defend the creativity but patterns how we saw in different examples [footnote] aren't needed or aren't useful in software development, because of the use and because could dead before they will be released to public domain and become useful. In software development, patterns don't have to be a handicap and the licenses must facilitate the use in developments.
				
			\end{itemize}
		\item Do you think GPL and free software licenses was threatened in any way? Why? (or why not?)
		
		Yes, I think the letter is against free software licenses and GPL appealing to the basic freedoms of the United States.\\
The letter describes them by putting them in the spotlight as a direct attack on freedom in more patriotic than scientific text. Defending the honour of the nation, ie defending tradition, a very strong argument because the phrase "if ever has done so well is because it is" whether to delve deeper into the same licenses which in turn defend authorship and knowledge facilitating it to people who want to use it.
	\end{enumerate}

\end{enumerate}


\begin{thebibliography}{9}

	\bibitem{ilaw}
		iLaw,\\
		SCO v IBM – Lessons for Developers,\\
		http://www.ilaw.com.au/public/scoarticle.html

	\bibitem{axxnet}
		Axxnet,\\
		SCO - Death Without Dignity,\\
		http://www.aaxnet.com/editor/edit032.html
	\bibitem{controversies}
	  Wikipedia,\\
	  SCO–Linux controversies.\\
	  http://en.wikipedia.org/wiki/SCO-Linux\_controversies.

	\bibitem{timeline}
		Wikipedia,\\
		Timeline of SCO–Linux controversies,\\
		http://en.wikipedia.org/wiki/Timeline\_of\_SCO-Linux\_controversies.

\end{thebibliography}
\end{document}
